\documentclass[a4paper,9pt]{article}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{margin=0.5in}
\usepackage{multicol}
\usepackage{titlesec}
\usepackage[normalem]{ulem} % For underlining, with normalem to prevent ulem from changing \emph

% Setting up itemize globally
\setlist[itemize]{noitemsep, topsep=0pt, leftmargin=*}

% Centering section titles
\titleformat{\section}[block]{\filcenter\large\bfseries}{\thesection}{1em}{}

% Custom command for underlining main section titles
\newcommand{\mainsection}[1]{\underline{#1}}

% Setting up hyperref to remove color and border around links
\hypersetup{
    colorlinks,
    linkcolor=black,
    filecolor=black,
    urlcolor=black,
    citecolor=black,
    allcolors=black
}

\begin{document}

% Name and contact information with location
\noindent
\begin{minipage}[t]{0.5\textwidth}
  \textbf{\huge Nima Nourinejad}\\
\end{minipage}%
\begin{minipage}[t]{0.5\textwidth}
  \raggedleft
  \begin{itemize}[label={},leftmargin=*,noitemsep]
    \item \textbf{Phone}: 045 177 4255
    \item \textbf{Email}: \href{mailto:nima.nourinejad@gmail.com}{nima.nourinejad@gmail.com}
    \item \textbf{LinkedIn}: \href{https://linkedin.com/in/nima-nourinejad}{linkedin.com/in/nima-nourinejad}
    \item \textbf{GitHub}: \href{https://github.com/nima-nourinejad}{github.com/nima-nourinejad}
    \item \textbf{English}: Advanced
  \end{itemize}
\end{minipage}

% Summary section with underlining
\section*{\mainsection{Summary}}
Passionate software developer with a foundation in full-stack JavaScript and C programming. Hands-on experience in
web development, system administration, and database management. Currently pursuing an IBM Full-Stack JavaScript
Developer Certificate and working on projects at Hive. Advanced English proficiency acquired through completing a
master’s degree in the UK and enhanced further by professional experience at LG International, where English was
the primary language of communication.

% Education and Certificates section with underlining
\section*{\mainsection{Education and Certificates}}
\begin{itemize}[leftmargin=*]
  \item \textbf{Hive Helsinki, Finland}: \textit{Software Development} (Expected 2024)
  \item \textbf{IBM (via Coursera)}: \textit{Full-Stack JavaScript Developer Certificate} (Expected 2024)
  \item \textbf{University of East Anglia, UK}: \textit{MSc Marketing} (2013)
  \item \textbf{Amirkabir University Of Technology, Iran}: \textit{BSc Mechanical Engineering} (2010)
\end{itemize}

% Skills section with underlining
\section*{\mainsection{Skills}}
\begin{itemize}[leftmargin=*]
  \item \textbf{Programming Languages}: JavaScript, Python, C, C++
  \item \textbf{Technologies}: Node.js, Express.js, MongoDB, React.js, FastAPI, PostgreSQL, SQL Server
  \item \textbf{Tools}: Git, GitHub, Agile, Scrum, VirtualBox, SELinux, AppArmor
  \item \textbf{Soft Skills}: Leadership, Project Management, Strategic Planning, Team Collaboration, Problem-Solving
  \item \textbf{Languages}: English (Advanced), Persian (Native)
\end{itemize}

% Projects and Achievements section with underlining
\section*{\mainsection{Projects and Achievements}}

% Subsection for IBM Certificate
\subsection*{IBM Full-Stack JavaScript Developer Professional Certificate}
\begin{multicols}{2}
\begin{itemize}[leftmargin=*]
  \item \textbf{Achieved Certificates}: 
    \begin{itemize}[leftmargin=*]
      \item JavaScript Programming Essentials
      \item Introduction to HTML, CSS, \& JavaScript
      \item Introduction to Software Engineering
      \item Getting Started with Git and GitHub\columnbreak
    \end{itemize}
  \item \textbf{Upcoming Courses}: Advanced JavaScript, Node.js, Express.js, MongoDB, React.js, API development, and DevOps.
\end{itemize}
\end{multicols}

% Subsection for Hive Projects
\subsection*{Hive Projects}
\setlength{\columnsep}{20pt} % Adjust the column separation
\begin{multicols}{2}
\begin{itemize}[leftmargin=*]
    \raggedcolumns % Ensure better alignment in the columns
    \item \textbf{Minishell}: Created a simple shell
    \item \textbf{So Long}: Developed a 2D game, learning texture and sprite management.
    \item \textbf{Pipex}: Implemented a UNIX pipeline mechanism.
    \item \textbf{Philosophers}: Simulated the dining philosophers problem.\columnbreak
     \vspace{\columnsep}
    \item \textbf{Born2beRoot}: System administration with virtualization and SELinux
    % Adjust the space between columns
    \item \textbf{Shell Exercises}: Developed efficient shell scripts.
    \item \textbf{Command Line Tools}: Created custom command-line tools.
    \item \textbf{Algorithmic Challenges}: Solved complex algorithmic problems.
  \end{itemize}
\end{multicols}

% Subsection for Python Intensive Course
\subsection*{Python Intensive Course at Hive}
\begin{itemize}[leftmargin=*]
  \item Completed projects covering basic and advanced Python programming, image processing, data handling, and package development.
\end{itemize}

% Other Online Courses section
\subsection*{Other Online Courses}
\begin{itemize}[leftmargin=*]
  \item HTML and CSS - SQL Server - PostgreSQL - FastAPI - Python - C Programming
\end{itemize}

% Experience section with underlining
\section*{\mainsection{Experience}}
\begin{itemize}[leftmargin=*]
  \item \textbf{Tavan Technology Tara, Tehran, Iran} \textit{Commercial Expert} (June 2018 - 3 years)
  \item \textbf{LG International, Tehran, Iran} \textit{Sales Expert} (April 2016 - 2 years)
\end{itemize}

\end{document}
